Specific leaf area explains difference in biomass partitioning between woody plant functional types

### 2014-10-07 manuscript/draftpaper.tex
More refs

\item There is no shortage of theoretical developments in understanding biomass allocation (WBE, \cite{franklin_modeling_2012}). In particular, theoretical work focusing on optimal partitioning theory is promising (e.g. \cite{valentine_modeling_2012}) but is yet to lead to operational models for dynamic global vegetation models.

@@

>>>>

\item There is no shortage of theoretical developments in understanding biomass allocation (\cite{cannell_carbon_1994,franklin_modeling_2012}, WBE). In particular, theoretical work focusing on optimal partitioning theory is promising (e.g. \cite{valentine_modeling_2012}) but is yet to lead to operational models for dynamic global vegetation models.

@@

\cite{cairns_root_1997} found no difference in root-shoot ratio between gymno and angio.

\cite{delucia_climate-driven_2000} LA/SA decreases with summer VPD for Pinus but not non-Pinus gymno. Also Pinus has much lower LA/SA than non-Pinus; suggesting that we should separate gymnosperms into those groups as well.
